###Packages
```{r packages required, echo = F, eval = F}
library(arm)
library(reshape)
library(reshape2)
library(lattice)
library(ggplot2)
library(MASS)
library(nlme)
library(lme4)
library(grid)
library(ggpubr)
library(extrafont)
```

##custom functions
```{r}
as.numeric.factor <- function(x) {as.numeric(levels(x))[x]}
```

##importing and cleaning up data
```{r Importing and cleaning up data, echo = F}
##read in the data

##nutrient data
dat <- read.csv("/Users/Jessica/Box Sync/ESE Lab Stuff/Susser/data NaP/2016 field season/data/summary.Na_addition.soil_samples.csv")

##cleaning up invalid data points
##sample had gdry_gwet greater than 1, subsequent measurements no good

##replacing column name "sample" with plot for consistancy
colnames(dat)[3] <- "plot"

##replacing letter codes with NA values (note that NS means that their is insufficient sample, NR means that the sample needs rerun. For the purposes of data analysis, both of these values are coded as NA, but for the purposes of sample processing these categoreis are kept seporate.)
dat[dat=="NR"] <- NA
dat[dat=="NS"] <- NA
dat[dat==""] <- NA

##making variables numeric
dat$p.bicarb <- as.numeric(as.character(dat$p.bicarb))
dat$p.h2o <- as.numeric(as.character(dat$p.h2o))
dat$p.fum <- as.numeric(as.character(dat$p.fum))
dat$p.k2so4 <- as.numeric(as.character(dat$p.k2so4))
dat$toc.k2so4 <- as.numeric(as.character(dat$toc.k2so4))
dat$tn.k2so4 <- as.numeric(as.character(dat$tn.k2so4))
dat$toc.h2o <- as.numeric(as.character(dat$toc.h2o))
dat$tn.h2o <- as.numeric(as.character(dat$tn.h2o))
dat$fum.c <- as.numeric(as.character(dat$fum.c))
dat$fum.n <- as.numeric(as.character(dat$fum.n))

##making factor variables factors
dat$treat.stover <- as.factor(dat$treat.stover)
dat$treat.na <- as.factor(dat$treat.na)

##making variables more readable
dat$treatment <- as.character(dat$treatment)
dat[dat == "cont"] <- "Control"
dat[dat == "na"] <- "Na"
dat[dat == "corn"] <- "Stover"
dat[dat == "both"] <- "Stover & Na"
dat$treatment <- as.factor(dat$treatment)

##replacing bout numbers with dates
dat$bout[dat$bout == 1] <- "20160714"
dat$bout[dat$bout == 2] <- "20160910"
dat$bout[dat$bout == 3] <- "20160930"

##make dates actual dates
dat$datecode <- as.Date(as.character(dat$datecode), "%Y%m%d")
dat$day <- format(dat$datecode, "%d-%b")

##creating microbial c, n, and p columns

dat$micro.p <- dat$p.fum - dat$p.k2so4
dat$micro.p[dat$micro.p < 0 ] <- 0.000001
dat$micro.c <- dat$fum.c - dat$toc.k2so4
dat$micro.n <- dat$fum.n - dat$tn.k2so4
dat$micro.c[dat$micro.c < 0] <- 0.000001
dat$micro.n[dat$micro.n < 0 ] <- 0.000001
dat$p.absorb <- dat$p.k2so4 - dat$p.h2o
dat$p.absorb[dat$p.absorb<0] <- 0.000001
dat$c.absorb <- dat$toc.k2so4 - dat$toc.h2o
dat$n.absorb <- dat$tn.k2so4 - dat$tn.h2o
dat$p.base <- dat$p.bicarb - dat$p.k2so4
dat$p.base[dat$p.base<0] <- 0.000001

##create a microbial c:n ratio
dat$micro.cn <- dat$micro.c/dat$micro.n
##create microbial c:p ratio
dat$micro.cp <- dat$micro.c/dat$micro.p

##Co2 produced per unit biomass C
dat$resp.bioc <- dat$co2/dat$micro.c
dat$resp.bioc[is.na(dat$fum.c)] <- NA
##getting rid of values where microibal biomass C is below detection
dat$resp.bioc[dat$micro.c < 0.001] <- NA

##making a total of all measured enzyme activity
dat$enz.tot <- dat$bg + dat$phos + dat$nag +dat$lap
##total N acquiring enzyme activity
dat$n.acquire <- dat$lap + dat$nag
##Get rid of BG data from contamination date
dat$bg[dat$datecode == "2016-07-13"] <- NA

##normalizing enzyme activity by microbial biomass
dat$bg.bioc <- dat$bg/dat$micro.c
dat$bg.bioc[dat$micro.c < 0.001] <- NA
dat$lap.bioc <- dat$lap/dat$micro.c
dat$lap.bioc[dat$micro.c < 0.001] <- NA
dat$nag.bioc <- dat$nag/dat$micro.c
dat$nag.bioc[dat$micro.c < 0.001] <- NA
dat$phos.bioc <- dat$phos/dat$micro.c
dat$phos.bioc[dat$micro.c < 0.001] <- NA

##making a column that is the p.h2o:p.bicarb
dat$p.h2o_bicarb <- dat$p.h2o/dat$p.bicarb
##comparing p.h2o by total p
dat$p.h2o_total <- dat$p.h2o/dat$p.total
##p.k2so4 over p.total
dat$p.k2so4_total <- dat$p.k2so4/dat$p.total
dat$p.bicarb_total <- dat$p.bicarb/dat$p.total
##bound P
dat$p.bound <- dat$p.total - (dat$p.bicarb + dat$micro.p)
##labile P that isn't adsorbed or non-adsorbed
dat$p.labile.other <- dat$p.bicarb - (dat$p.absorb + dat$p.h2o)
##absorbed p over  total
dat$p.absorb_total <- dat$p.absorb/dat$p.total
##p microbial/ total
dat$micro.p_total <- dat$micro.p/dat$p.total
dat$p.base_total <- dat$p.base/dat$p.total
dat$p.bound_total <- dat$p.bound/dat$p.total
dat$micro.p_total <- dat$micro.p/dat$p.total

##create a variable for moisture content (which is 1-dry weight)
dat$moist <- 1 - dat$gdry_gwet
dat$moist[dat$moist < 0] <- NA
dat$moist.percent <- 100*dat$moist
##read in resin strip data
resin <- read.csv("/Users/Jessica/Box Sync/ESE Lab Stuff/Susser/data NaP/2016 field season/data/summary.Na_addition.resin.csv")
resin[resin=="NR"] <- NA
resin[resin=="NS"] <- NA
resin$toc.resin <- as.numeric(as.character(resin$toc.resin))
resin$tn.resin <- as.numeric(as.character(resin$tn.resin))
resin$p.resin <- as.numeric(as.character(resin$p.resin))
resin$toc.resin_sum <- resin$toc.resin * resin$days
resin$tn.resin_sum <- resin$tn.resin* resin$days
resin$p_sum.resin <- resin$p.resin * resin$days

##invert dat

##community data
com <- read.csv("/Users/Jessica/Box Sync/ESE Lab Stuff/Susser/data NaP/2016 field season/data/community_all.csv")
com$plot <- NULL
colnames(com)[1] <- "plot"

##making variables more readable
com$treatment <- as.character(com$treatment)
com[com == "control"] <- "Control"
com[com == "na"] <- "Na"
com[com == "corn"] <- "Stover"
com[com == "both"] <- "Stover & Na"
com$treatment <- as.factor(com$treatment)
com$na <- NA
com$na[com$treatment == "Control"] <- F
com$na[com$treatment == "Na"] <- T
com$na[com$treatment == "Stover"] <- F
com$na[com$treatment == "Stover & Na"] <- T
com$na <- as.factor(com$na)

com$stover <- NA
com$stover[com$treatment == "Control"] <- F
com$stover[com$treatment == "Na"] <- F
com$stover[com$treatment == "Stover"] <- T
com$stover[com$treatment == "Stover & Na"] <- T
com$stover <- as.factor(com$stover)
##adding block to com data
com$block <- NA
com$block[com$plot <= 4] <- 1
com$block[com$plot > 4 & com$plot <= 8] <- 2
com$block[com$plot > 8 & com$plot <= 12] <- 3
com$block[com$plot > 12 & com$plot <= 16] <- 4
com$block[com$plot > 16 & com$plot <= 20] <- 5
com$block[com$plot > 20 & com$plot <= 24] <- 6
com$block[com$plot > 24 & com$plot <= 28] <- 7
com$block[com$plot > 28 & com$plot <= 32] <- 8
com$block[com$plot > 32 & com$plot <= 36] <- 9
com$block[com$plot > 36 & com$plot <= 40] <- 10
com$block[com$plot > 40 & com$plot <= 44] <- 11
com$block[com$plot > 44 & com$plot <= 48] <- 12
```

##combining invert and soil nutrient data

###sum all of the invert data for each plot for all of the dates
```{r}
com.melted <- melt(com, id.vars = c("plot", "treatment", "field", "na", "stover", "date", "block"))
com.plot <- cast(com.melted, plot + field + treatment + block~variable, sum, na.rm=T)
com.average <- cast(com.melted, plot + field + treatment + block ~ variable, mean, na.rm = T)
##making variables more readable
com.plot$treatment <- as.character(com.plot$treatment)
com.plot[com.plot == "control"] <- "Control"
com.plot[com.plot == "na"] <- "Na"
com.plot[com.plot == "corn"] <- "Stover"
com.plot[com.plot == "both"] <- "Stover & Na"
com.plot$treatment <- as.factor(com.plot$treatment)
```



##create a column in the soils data that is the average capture rate of inverts
```{r}
dat$abundance <- rep(com.average$abundance, times = 3)
```


##creating a subset for each sampling date for soil samples

```{r}
dat.b1 <- subset(dat, bout == "20160714")
dat.b2 <- subset(dat, bout == "20160910")
dat.b3 <- subset(dat, bout == "20160930")
```


##get a cumulative resin value
```{r}
colnames(resin)[2] <- "plot"
resin.melted <- melt(resin, id.vars = c("date", "plot", "block", "field", "treatment", "na", "stover"))
resin.sum <- cast(resin.melted, plot  ~ variable, fun.aggregate = sum)
```

##getting averages of soil nutrient data
```{r}
colnames(dat)[3] <- "plot"
dat.melted <- melt(dat, id.vars = c("bout", "datecode", "plot", "block", "field", "treatment", "treat.na", "treat.stover"))
dat.melted$value <- as.numeric(dat.melted$value)
dat.plot <- cast(dat.melted, plot + field + treatment + block + treat.na + treat.stover ~ variable, fun.aggregate = mean, na.action = na.rm)
dat.plot$p.total.begin <- dat$p.total[dat$bout == 20160714]
dat.plot$p.total.end <- dat$p.total[dat$bout == 20160930]
dat.plot$p.total.change <- dat.plot$p.total.begin - dat.plot$p.total.end
dat.plot$p.h2o.begin <- dat$p.h2o[dat$bout == 20160714]
dat.plot$p.h2o.end <- dat$p.h2o[dat$bout == 20160930]
dat.plot$p.h2o.change <- dat.plot$p.h2o.begin - dat.plot$p.h2o.end
dat.plot$p.bicarb.begin <- dat$p.bicarb[dat$bout == 20160714]
dat.plot$p.bicarb.end <- dat$p.bicarb[dat$bout == 20160930]
dat.plot$p.bicarb.change <- dat.plot$p.bicarb.begin - dat.plot$p.bicarb.end
dat.plot$p.k2so4.begin <- dat$p.k2so4[dat$bout == 20160714]
dat.plot$p.k2so4.end <- dat$p.k2so4[dat$bout == 20160930]
dat.plot$p.k2so4.change <- dat.plot$p.k2so4.begin-dat.plot$p.k2so4.end
dat.plot$p.absorb.begin <- dat$p.absorb[dat$bout == 20160714]
dat.plot$p.absorb.end <- dat$p.absorb[dat$bout == 20160930]
dat.plot$p.absorb.change <- dat.plot$p.absorb.begin-dat.plot$p.absorb.end
dat.plot$p.base.begin <- dat$p.base[dat$bout == 20160714]
dat.plot$p.base.end <- dat$p.base[dat$bout == 20160930]
dat.plot$p.base.change <- dat.plot$p.base.begin-dat.plot$p.base.end
dat.plot$p.bound.begin <- dat$p.bound[dat$bout == 20160714]
dat.plot$p.bound.end <- dat$p.bound[dat$bout == 20160930]
dat.plot$p.bound.change <- dat.plot$p.bound.begin-dat.plot$p.bound.end
dat.plot$p.total.average <- (dat$p.total[dat$bout == 20160714] + dat$p.total[dat$bout == 20160930])/2
dat.plot$c.percent.average <- (dat$c.percent[dat$bout == 20160714] + dat$c.percent[dat$bout == 20160930])/2
dat.plot$n.percent.average <- (dat$n.percent[dat$bout == 20160714] + dat$n.percent[dat$bout == 20160930])/2
dat.plot$p.h2o_p.total <- (dat$p.h2o_total[dat$bout == 20160714] + dat$p.h2o_total[dat$bout == 20160930])/2
dat.plot$p.absorb_total <- (dat$p.absorb_total[dat$bout == 20160714]+ dat$p.absorb_total[dat$bout == 20160930])/2
dat.plot$p.bicarb_total <- (dat$p.bicarb_total[dat$bout == 20160714]+ dat$p.bicarb_total[dat$bout == 20160930])/2
dat.plot$p.base_total <- (dat$p.base_total[dat$bout == 20160714]+ dat$p.base_total[dat$bout == 20160930])/2
dat.plot$p.bound_total <- (dat$p.bound_total[dat$bout == 20160714]+ dat$p.bound_total[dat$bout == 20160930])/2
dat.plot$toc.k2so4.begin <- dat$toc.k2so4[dat$bout == 20160714]
dat.plot$toc.k2so4.end <- dat$toc.k2so4[dat$bout == 20160930]
dat.plot$toc.k2so4.change <- dat.plot$toc.k2so4.end - dat.plot$toc.k2so4.begin
bwplot(toc.k2so4.change ~ treatment, data = dat.plot)
```

##functional group and taxa
```{r}
group <- read.csv("/Users/Jessica/Box Sync/ESE Lab Stuff/Susser/data NaP/2016 field season/data/functional.group_all.csv")
group$treatment <- as.character(group$treatment)
group[group == "control"] <- "Control"
group[group == "na"] <- "Na"
group[group == "corn"] <- "Stover"
group[group == "both"] <- "Stover & Na"
group$treatment <- factor(group$treatment)
group$treat.stover <- NA
group$treat.stover[group$treatment == "Na" | group$treatment == "Control"] <- 0
group$treat.stover[group$treatment == "Stover" | group$treatment == "Stover & Na"] <- 1
group$treat.stover <- factor(group$treat.stover)
group$treat.na <- NA
group$treat.na[group$treatment == "Control" | group$treatment == "Stover"] <- 0
group$treat.na[group$treatment == "Na" | group$treatment == "Stover & Na"] <- 1
group$treat.na <- factor(group$treat.na)
order <- read.csv("/Users/Jessica/Box Sync/ESE Lab Stuff/Susser/data NaP/2016 field season/data/order_all.csv")
group.melted <- melt(group, id.vars = c("plot.number", "plot", "date", "treatment", "field"))
group.melted$value <- as.numeric(group.melted$value)
group.sum <- cast(group.melted, plot.number + treatment + field ~ variable, fun.aggregate = sum)
group.sum$abundance <- com.plot$abundance
group.sum$block <- NA
group.sum$block[group.sum$plot.number <= 4] <- 1
group.sum$block[group.sum$plot.number > 4 & group.sum$plot.number <= 8] <- 2
group.sum$block[group.sum$plot.number > 8 & group.sum$plot.number <= 12] <- 3
group.sum$block[group.sum$plot.number > 12 & group.sum$plot.number <= 16] <- 4
group.sum$block[group.sum$plot.number > 16 & group.sum$plot.number <= 20] <- 5
group.sum$block[group.sum$plot.number > 20 & group.sum$plot.number <= 24] <- 6
group.sum$block[group.sum$plot.number > 24 & group.sum$plot.number <= 28] <- 7
group.sum$block[group.sum$plot.number > 28 & group.sum$plot.number <= 32] <- 8
group.sum$block[group.sum$plot.number > 32 & group.sum$plot.number <= 36] <- 9
group.sum$block[group.sum$plot.number > 36 & group.sum$plot.number <= 40] <- 10
group.sum$block[group.sum$plot.number > 40 & group.sum$plot.number <= 44] <- 11
group.sum$block[group.sum$plot.number > 44 & group.sum$plot.number <= 48] <- 12
group.sum$block <- as.factor(group.sum$block)
family <- read.csv("/Users/Jessica/Box Sync/ESE Lab Stuff/Susser/data NaP/2016 field season/data/family_all.csv")
```
##merging inverts and nutrient data, merges average soil nutrient values with cumulative abundance
```{r}
dc.plot <- merge(com.plot, dat.plot, by = c("plot", "field", "treatment"))
dc.plot <- merge(dc.plot, resin.sum, by = c("plot"))
dc.plot$p.total <- (dat.b1$p.total + dat.b3$p.total)/2
colnames(dc.plot)[3] <- "treatment"
colnames(group.sum)[1] <- "plot"
dc.plot <- merge(dc.plot, group.sum, by = "plot")
dc.plot$block.y <- NULL
dc.plot$predator <- group.sum$predator
dc.plot$herbivore <- group.sum$herbivore
dc.plot$scavenger <- group.sum$scavenger
dc.plot$field.y <- NULL
colnames(dc.plot)[2] <- "field"
colnames(dc.plot)[3]  <- "treatment"
dc.plot$block.y <- NULL
```


##functional group and taxa
```{r}
group <- read.csv("/Users/Jessica/Box Sync/ESE Lab Stuff/Susser/data NaP/2016 field season/data/functional.group_all.csv")
group$treatment <- as.character(group$treatment)
group[group == "control"] <- "Control"
group[group == "na"] <- "Na"
group[group == "corn"] <- "Stover"
group[group == "both"] <- "Stover & Na"
group$treatment <- factor(group$treatment)
group$treat.stover <- NA
group$treat.stover[group$treatment == "Na" | group$treatment == "Control"] <- 0
group$treat.stover[group$treatment == "Stover" | group$treatment == "Stover & Na"] <- 1
group$treat.stover <- factor(group$treat.stover)
group$treat.na <- NA
group$treat.na[group$treatment == "Control" | group$treatment == "Stover"] <- 0
group$treat.na[group$treatment == "Na" | group$treatment == "Stover & Na"] <- 1
group$treat.na <- factor(group$treat.na)
order <- read.csv("/Users/Jessica/Box Sync/ESE Lab Stuff/Susser/data NaP/2016 field season/data/order_all.csv")
group.melted <- melt(group, id.vars = c("plot.number", "plot", "date", "treatment", "field"))
group.melted$value <- as.numeric(group.melted$value)
group.sum <- cast(group.melted, plot.number + treatment + field ~ variable, fun.aggregate = sum)
group.sum$abundance <- com.plot$abundance
group.sum$block <- NA
group.sum$block[group.sum$plot.number <= 4] <- 1
group.sum$block[group.sum$plot.number > 4 & group.sum$plot.number <= 8] <- 2
group.sum$block[group.sum$plot.number > 8 & group.sum$plot.number <= 12] <- 3
group.sum$block[group.sum$plot.number > 12 & group.sum$plot.number <= 16] <- 4
group.sum$block[group.sum$plot.number > 16 & group.sum$plot.number <= 20] <- 5
group.sum$block[group.sum$plot.number > 20 & group.sum$plot.number <= 24] <- 6
group.sum$block[group.sum$plot.number > 24 & group.sum$plot.number <= 28] <- 7
group.sum$block[group.sum$plot.number > 28 & group.sum$plot.number <= 32] <- 8
group.sum$block[group.sum$plot.number > 32 & group.sum$plot.number <= 36] <- 9
group.sum$block[group.sum$plot.number > 36 & group.sum$plot.number <= 40] <- 10
group.sum$block[group.sum$plot.number > 40 & group.sum$plot.number <= 44] <- 11
group.sum$block[group.sum$plot.number > 44 & group.sum$plot.number <= 48] <- 12
group.sum$block <- as.factor(group.sum$block)
family <- read.csv("/Users/Jessica/Box Sync/ESE Lab Stuff/Susser/data NaP/2016 field season/data/family_all.csv")
```
