---
title: "redoing mixed effects models"
output:
  html_document: default
  html_notebook: default
---
#packages
```{r}
library(nlme)
library(lsmeans)
```

#treatment effect on c.percent and Na+
```{r}
##c.percent
hist(dat$c.percent)
hist(log(dat$c.percent))
bwplot(c.percent ~ treatment|bout, data = dat)
barchart(c.percent ~ treatment | bout, data = dat)
c1 <- lm((c.percent)  ~ treatment + bout, data = dat)
summary(c1)
plot(c1)
##DOC
hist(dat$toc.k2so4)
hist(log(dat$toc.k2so4))
c2 <- lm(log(toc.k2so4) ~ treatment * bout, data = dat)
summary(c2)
anova(c2)
plot(c2)
class(dat$bout)
datc <- dat
class(datc$bout)
datc$bout <- as.factor(datc$bout)
levels(datc$bout)
datc$bout <-ordered(datc$bout, levels = c("20160930", "20160714", "20160910"))
c3 <- lm(log(toc.h2o) ~ treatment * bout, data = datc)
bwplot(toc.h2o ~ treatment|bout, data = dat)
summary(c3)
plot(c3)
##NA
na1 <- lm(na ~ treatment * bout, data = dat)
summary(na1)
anova(na1)
xyplot(toc.k2so4 ~ toc.h2o | bout, data = dat, type = c("p"), groups = treatment, auto.key = T)
```

#microbial measurements
##microbial respiration
```{r}
aggregate(co2~treatment + bout, data = dat, FUN = mean)
mr4 <- lme(log(co2) ~ treatment * bout, random = ~1|field/block, data = subset(dat, co2 > 0.001), na.action = na.omit)
summary(mr4)
lsmeans(mr4, list(pairwise ~ treatment) )
pairs(mr4)
##getting the p-value for difference between stover and stover & Na
dat5 <- dat
print(levels(dat5$treatment))

dat5$treatment <- ordered(dat5$treatment, levels = c("Stover", "Na", "Control", "Stover & Na"))
levels(dat5$treatment)
mr5 <- lme(log(co2) ~ treatment * bout, random = ~1|field/block, data = subset(dat5, co2 > 0.001), na.action = na.omit)
summary(mr5)
```

##microbial biomass C
```{r}
mb1 <- lme(log(micro.c)~treatment * bout, random = ~1|field/block, data = subset(dat, micro.c > 0.0001), na.action = na.omit, method = "ML")
summary(mb1)
plot(mb1)
qqnorm(mb1)
qqnorm(resid(mb1))
##no significant interaction
mb2 <- lme(log(micro.c)~treatment + bout, random = ~1|field/block, data = subset(dat, micro.c > 0.0001), na.action = na.omit, method = "ML")
summary(mb2)
plot(mb2)
qqnorm(mb2)
anova(mb1, mb2)
```



##microbial biomass N
```{r}
mn1 <- lme(log(micro.n) ~ treatment * bout, random = ~1|field/block, data = subset(dat, micro.n > 0.001), na.action = na.omit)
summary(mn1)
##no significant interaction
mn2 <- lme(log(micro.n) ~ treatment + bout, random = ~1|field/block, data = subset(dat, micro.n > 0.001), na.action = na.omit)
summary(mn2)
plot(mn2)
qqnorm(mn2)
qqnorm(resid(mn2))
```

##microbial biomass P
```{r}
mp2 <- lme(log(micro.p)~ treatment * bout, random = ~1|field/block, data = subset(dat, micro.p > 0.0001), na.action = na.omit)
summary(mp2)
##no significant interaction
mp1 <- lme(log(micro.p)~ treatment + bout, random = ~1|field/block, data = subset(dat, micro.p > 0.0001), na.action = na.omit)
summary(mp1)
plot(mp1)
qqnorm(mp1)
```

##enzyme activities
###total enzyme activity
```{r}
te1 <- lme(log(enz.tot) ~ treatment * bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(te1)
plot(te1)
qqnorm(te1)
aggregate(enz.tot~treatment + bout, data = dat, FUN = mean)
bwplot(enz.tot ~ treatment| bout, data = dat)
```


###bg activities

```{r}
bg1 <- lme(log(bg) ~ treatment * bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(bg1)
plot(bg1)
qqnorm(bg1)
aggregate(bg~treatment + bout, data = dat, FUN = function(x) c(mean=mean(x), sd = sd(x), n = length(x)))
bwplot(bg~treatment | bout, data = dat)
```

###N aq actiities
```{r}
nq1 <- lme(log(n.acquire) ~ treatment * bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(nq1)
plot(nq1)
qqnorm(nq1)
bwplot(n.acquire ~ treatment|bout, data = dat)
```

###phos activities
```{r}
phos1 <- lme(log(phos) ~ treatment * bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(phos1)
plot(phos1)
qqnorm(phos1)
bwplot(phos~treatment|bout, data = dat)
```




#invert measurements
##overall abundance
```{r}
a1 <- glmer(abundance ~ treatment + (1|field/block), data = com.plot, na.action = na.omit, family = poisson)
summary(a1)
plot(a1)
qqnorm(resid(a1))
mean(na.omit(group.sum$abundance[group.sum$treatment == "Control"]))
plot(abundance ~ treatment, data = com.plot)
```

##predator
```{r}
p1 <- glmer(predator ~ treatment + (1|field/block), data = group.sum, na.action = na.omit, family = poisson)
summary(p1)
plot(p1)
qqnorm(resid(p1))
group.sum$block
```

##scavanger
```{r}
s1 <- glmer(scavenger ~ treatment + (1|field/block), data = group.sum, na.action = na.omit, family = poisson)
summary(s1)
plot(s1)
qqnorm(resid(s1))
```

##herbivore
```{r}
h1 <- glmer(herbivore ~ treatment + (1|field/block), data = group.sum, na.action = na.omit, family = poisson)
summary(h1)
plot(h1)
qqnorm(resid(h1))
```



#p pools v. treatment
##p.h2o
```{r}
ph1 <- lme(log(p.h2o) ~ treatment + moist + pH + bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(ph1)
plot(ph1)
qqnorm(ph1)

```
##p.absorbed
```{r}
pa1 <- lme(log(p.absorb) ~ treatment + moist + pH + bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(pa1)
plot(pa1)
qqnorm(pa1)
```

##p.bicarb
```{r}
pb1 <- lme(log(p.bicarb) ~ treatment + moist + pH + bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(pb1)
plot(pb1)
qqnorm(pb1)
```


##p.base
```{r}
pba1 <- lme(log(p.base) ~ treatment + moist + pH + bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(pba1)
plot(pba1)
qqnorm(pba1)
```


##p.bound
```{r}
pbo1 <- lme(log(p.bound) ~ treatment + moist + pH + bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(pbo1)
pbo2 <- lme(log(p.bound) ~ treatment + pH + bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(pbo2)
plot(pbo2)
qqnorm(pbo2)
```

##p.total
```{r}
pt1 <- lme(log(p.total) ~ treatment + moist + pH + bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(pt1)
pt2 <- lme(log(p.total) ~ treatment + bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(pt2)
plot(pt2)
qqnorm(pt2)
bwplot(p.total~treatment|field+bout, data = dat)
```

##p.resin
```{r}
pr1 <- lme(log(p.resin) ~ treatment + moist + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
summary(pr1)
plot(pr1)
qqnorm(pr1)
```

##p.micro
```{r}
pm1 <- lme(log(micro.p) ~ treatment + moist.percent + pH + bout, random = ~1|field/block, data = subset(dat, micro.p > 0.000001), na.action = na.omit)
plot(pm1)
qqnorm(pm1)
summary(pm1)
```


#p pool proportions
##p.h2o/total
```{r}
pht1 <- lme(log(p.h2o_total) ~ treatment + moist + pH + bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(pht1)
dat$moist.percent <- 100*dat$moist
pht2 <- lme(log(p.h2o_total) ~ treatment + moist.percent + bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(pht2)
plot(pht2)
qqnorm(pht2)
bwplot(p.h2o_total ~ bout|block, data = dat)
```
##p.absorb_total
```{r}
pat1 <- lme(log(p.absorb_total) ~ treatment + moist.percent + pH + bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(pat1)
plot(pat1)
qqnorm(pat1)
```
So this model doesn't work very well
###dealing with the threshold
so overall, the k2so4 P pool is not significantly different from the water-extractable pool. However, this relationship breaks down above a certain threshold. Let's try to figure out what that threshold is.

```{r}
xyplot(p.k2so4~p.total, data = dat)
xyplot(p.absorb ~ p.total, data = dat)
t.test(dat$p.k2so4, dat$p.h2o, paired = T)
hp1 <- subset(dat, p.total > 875)
t.test(hp1$p.k2so4, hp1$p.h2o, paired = T)
hp2 <- subset(dat, p.total > 900)
t.test(hp2$p.k2so4, hp2$p.h2o, paired = T)
hp3 <- subset(dat, p.total > 880)
t.test(hp3$p.k2so4, hp3$p.h2o, paired = T)
xyplot(p.k2so4 ~ p.total, data = hp1, groups = treatment)
xyplot(p.k2so4 ~ p.total, data = hp2)
xyplot(p.k2so4 ~ p.total, data = hp3)
```

Okay, so a threshold around 875 seems reasonable

```{r}
bwplot(p.absorb_total~treatment, data = hp1)
bwplot(p.absorb_total~treatment | bout, data = hp1)
summary(aov(p.absorb_total ~ treatment, data = hp1))
summary(lm(p.absorb_total ~ treatment + bout, data = hp1))
a1 <- lme(log(p.absorb_total) ~ treatment + moist.percent + pH + bout, random = ~1|field, data = hp1, na.action = na.omit)
plot(a1)
qqnorm(a1)
summary(a1)
xyplot(p.absorb ~ p.total, data = hp1, groups = treatment, type = c("p", "r"))
```



##p.bicarb_total
```{r}
pot1 <- lme(log(p.bicarb_total) ~ treatment + moist.percent + pH + bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(pot1)
plot(pot1)
qqnorm(pot1)
```

##p.base_total
```{r}
pbt1 <- lme(log(p.base_total) ~ treatment + moist + pH + bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(pbt1)
plot(pbt1)
qqnorm(pbt1)
```


##p.bound
```{r}
pbt1 <- lme(log(p.bound_total) ~ treatment + moist.percent + pH + bout, random = ~1|field/block, data = dat, na.action = na.omit)
summary(pbt1)
plot(pbt1)
qqnorm(pbt1)
```


##micro.p
```{r}
pmt1 <- lme(log(micro.p_total) ~ treatment + moist + pH + bout, random = ~1|field/block, data = subset(dat, micro.p > 0.00001), na.action = na.omit)
summary(pmt1)
```

#changes in p pools
##p.h2o
```{r}
phc1 <- lme((p.h2o.change) ~ treatment + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
summary(phc1)
plot(phc1)
qqnorm(phc1)
```

##p.absorb
```{r}
pac1 <- lme((p.absorb.change) ~ treatment + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
summary(pac1)
qqnorm(pac1)
plot(pac1)
xyplot(p.absorb.change ~ p.total, data = dc.plot)
View(b1)
```

okay, but again it looks like we don't have a significant pool when p.total > 875. So let's do that again

###desling with  threshold
```{r}
pac2 <- lme((p.absorb.change) ~ treatment, random = ~1|field/block.x, data = subset(dc.plot, p.total > 875), na.action = na.omit)
plot(pac2)
qqnorm(pac2)
summary(pac2)
xyplot(p.absorb.change ~ p.total|field, data = subset(dc.plot, p.total > 875), groups = treatment, auto.key = T)
```

##p.bicarb
```{r}
poc1 <- lme((p.bicarb.change) ~ treatment + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
summary(poc1)
plot(poc1)
qqnorm(poc1)
```


##p.base
```{r}
pbc1 <- lme((p.base.change) ~ treatment + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
summary(pbc1)
plot(pbc1)
qqnorm(pbc1)
```

##p.bound
```{r}
pnc1 <- lme((p.bound.change) ~ treatment + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
summary(pnc1)
plot(pnc1)
qqnorm(pnc1)
```

##p.total
```{r}
ptc1 <- lme((p.total.change) ~ treatment + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
summary(ptc1)
plot(ptc1)
qqnorm(ptc1)
```



#p pools v. micro
##p.h2o
###p.h2o v. co2
```{r}
hr1 <- lme(log(p.h2o_total) ~ log(co2) + pH + moist.percent + bout, random = ~1|field/plot, data = dat, na.action = na.omit)
summary(hr1)
plot(hr1)
qqnorm(hr1)
```

###p.h2o v. biomass
```{r}
hc1 <- lme(log(p.h2o_total) ~ log(micro.c) + pH + moist.percent + bout, random = ~1|field/plot, data = dat, na.action = na.omit)
summary(hc1)
plot(hc1)
qqnorm(hc1)
hc2 <- lme(log(p.h2o_total) ~ log(micro.c) + moist.percent + bout, random = ~1|field/plot, data = dat, na.action = na.omit)
summary(hc2)
plot(hc2)
qqnorm(hc2)
```


###p.h2o v. phos
```{r}
hp1 <- lme(log(p.h2o_total) ~ log(phos) + pH + moist.percent + bout, random = ~1|field/plot, data = dat, na.action = na.omit)
summary(hp1)
hp2 <- lme(log(p.h2o_total) ~ log(phos) + moist.percent + bout, random = ~1|field/plot, data = dat, na.action = na.omit)
summary(hp2)
```


##p.absorb
###p.absorb v. co2
```{r}
ra1 <- lme(log(p.absorb_total) ~ log(co2) + pH + moist.percent + bout, random = ~1|field/plot, data = subset(dat, p.total > 875), na.action = na.omit)
summary(ra1)
plot(ra1)
qqnorm(ra1)
```
###p.absorb v. micro.c
```{r}
ca1 <- lme(log(p.absorb_total) ~ log(micro.c) + pH + moist.percent + bout, random = ~1|field/plot, data = subset(dat, p.total > 875), na.action = na.omit)
summary(ca1)
plot(ca1)
qqnorm(ca1)
```
###p.absorb v. phos
```{r}
pa1 <- lme(log(p.absorb_total) ~ log(phos) + pH + moist.percent + bout, random = ~1|field/plot, data = subset(dat, p.total > 875), na.action = na.omit)
summary(pa1)
plot(pa1)
qqnorm(pa1)
```


##p.bicarb
###p.bicarb v. co2
```{r}
or1 <- lme(log(p.bicarb_total) ~ log(co2) + pH + moist.percent + bout, random = ~1|field/plot, data = dat, na.action = na.omit)
summary(or1)
plot(or1)
qqnorm(or1)
```
###p.bicarb v. biomass
```{r}
oc1 <- lme(log(p.bicarb_total) ~ log(micro.c) + pH + moist.percent + bout, random = ~1|field/plot, data = dat, na.action = na.omit)
summary(oc1)
plot(oc1)
qqnorm(oc1)
```
###p.bicarb v. phos

```{r}
op1 <- lme(log(p.bicarb_total) ~ log(phos) + pH + moist.percent + bout, random = ~1|field/plot, data = dat, na.action = na.omit)
summary(op1)
qqnorm(op1)
plot(op1)
```

##p.base
###p.base v. co2
```{r}
bc1 <- lme(log(p.base_total) ~ log(co2) + pH + moist.percent + bout, random = ~1|field/plot, data = dat, na.action = na.omit)
summary(bc1)
plot(bc1)
qqnorm(bc1)
```

###p.base v. micro.c
```{r}
bb1 <- lme(log(p.base_total) ~ log(micro.c) + pH + moist.percent + bout, random = ~1|field/plot, data = dat, na.action = na.omit)
summary(bb1)
plot(bb1)
qqnorm(bb1)
```

###p.base v. phos
```{r}
bp1 <- lme(log(p.base_total) ~ log(phos) + pH + moist.percent + bout, random = ~1|field/plot, data = dat, na.action = na.omit)
summary(bp1)
plot(bp1)
qqnorm(bp1)
```

##p.bound
###p.bound v. co2
```{r}
br1 <- lme(log(p.bound_total) ~ log(co2) + pH +  bout, random = ~1|field/plot, data = dat, na.action = na.omit)
summary(br1)
qqnorm(br1)
plot(br1)
```
###p.bound v. micro.c
```{r}
bc1 <- lme(log(p.bound_total) ~ log(micro.c) + pH + bout, random = ~1|field/plot, data = dat, na.action = na.omit)
summary(bc1)
plot(bc1)
```

###p.bound v. phos
```{r}
bp1 <- lme(log(p.bound_total) ~ log(phos) + pH + moist.percent + bout, random = ~1|field/plot, data = dat, na.action = na.omit)
summary(bp1)
plot(bp1)
qqnorm(bp1)
```


##p.resin
###p.resin v.  average co2
```{r}
prr1 <- lme(log(p.resin) ~ log(co2) + pH, random = ~1|field, data = dc.plot, na.action = na.omit)
summary(prr1)
plot(prr1)
qqnorm(prr1)
xyplot(p.resin ~ co2, data = dc.plot, type = c("p", "r"))
hist(log(dc.plot$p.resin))
```
###p.resin v. micro.c
```{r}
prc1 <- lme(log(p.resin) ~ log(micro.c) + pH, random = ~1|field, data = dc.plot, na.action = na.omit)
summary(prc1)
plot(prc1)
qqnorm(prc1)
```

###p.resin v. phos
```{r}
prp1 <- lme(log(p.resin) ~ log(phos) + pH, random = ~1|field, data = dc.plot, na.action = na.omit)
summary(prp1)
```


#p pools v. invert
##p.h2o v. invert
###p.h2o v. abundance
```{r}
ah1 <- lme(p.h2o ~ abundance.x + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
summary(ah1)
plot(ah1)
qqnorm(ah1)
```
###p.h2o v. herbivore
```{r}
hh1 <- lme(p.h2o ~ herbivore + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
summary(hh1)
plot(hh1)
qqnorm(hh1)
```
###p.h2o v. predator
```{r}
ph1  <- lme(p.h2o ~ predator + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
summary(ph1)
plot(ph1)
qqnorm(ph1)
```

###p.h2o v. scavenger
```{r}
sh1 <- lme(p.h2o ~ scavenger + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
summary(sh1)
plot(sh1)
qqnorm(sh1)
```

##p.absorb v. invert
###p.absorb v. abundance
```{r}
aa1 <- lme(p.absorb_total ~ abundance.x + pH, random = ~1|field/block.x, data = subset(dc.plot, p.total > 875), na.action = na.omit)
plot(aa1)
qqnorm(aa1)
summary(aa1)
xyplot(p.absorb ~ abundance.x, data = subset(dc.plot, p.total > 875))
```
###p.absorb v. herbivore
```{r}
ha1 <- lme(p.absorb_total ~ herbivore, random = ~1|field/block.x, data = subset(dc.plot, p.total > 875), na.action = na.omit)
summary(ha1)
xyplot(p.absorb_total ~ herbivore, data = dc.plot)
plot(ha1)
qqnorm(ha1)
xyplot(p.absorb_total ~ p.total, data = dc.plot)
xyplot(p.total ~ herbivore, data = subset(dc.plot, p.total > 875))
xyplot(p.total ~ herbivore, data = dc.plot)
xyplot(herbivore~ p.total, data = dc.plot, group = field)
```
###p.absorb v. predator
```{r}
pa1 <- lme(p.absorb_total ~ predator, random = ~1|field/block.x, data = subset(dc.plot, p.total > 875), na.action = na.omit)
summary(pa1)
plot(pa1)
qqnorm(pa1)
xyplot(p.absorb_total ~ predator, data = subset(dc.plot,p.total > 875), type = c("p", "r"))
```
###p.absorb v. scavenger
```{r}
sa1 <- lme(p.absorb_total ~ scavenger, random = ~1|field/block.x, data = subset(dc.plot, p.total > 875), na.action = na.omit)
summary(sa1)
qqnorm(sa1)
plot(sa1)
xyplot(p.absorb_total ~ scavenger, data = subset(dc.plot, p.total > 875))
hist(dc.plot$scavenger)
```

##p.olsen v. fauna
###p.olsen v. abundance
```{r}
oa1 <- lme(p.bicarb_total ~ abundance.x + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
summary(oa1)
plot(oa1)
qqnorm(oa1)
```
###p.olsen v. herbivore
```{r}
oh1 <- lme(p.bicarb_total ~ herbivore + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
summary(oh1)
plot(oh1)
qqnorm(oh1)
```
###p.olsen v. predator
```{r}
op1 <- lme(p.bicarb_total ~ predator + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(op1)
qqnorm(op1)
summary(op1)
```
###p.olsen v. scavenger
```{r}
os1 <- lme(p.bicarb_total ~ scavenger + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
qqnorm(os1)
plot(os1)
summary(os1)
```

##p.base v. fauna
###p.base v.abundance
```{r}
ba1 <- lme(p.base_total ~ abundance.x + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(ba1)
qqnorm(ba1)
summary(ba1)
xyplot(p.base_total ~ abundance.x, data = dc.plot)
```
###p.base v. herbivore
```{r}
bh1 <- lme(p.base_total ~ herbivore + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(bh1)
qqnorm(bh1)
xyplot(p.base_total ~ herbivore, data = dc.plot, type = c("p", "r"))
summary(bh1)
```
###p.base v. predator
```{r}
bp1 <- lme(p.base_total ~ predator + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(bp1)
qqnorm(bp1)
xyplot(p.base_total ~ predator, data = dc.plot, type = c("p", "r"))
summary(bp1)
```
###p.base v. scavenger
```{r}
bs1 <- lme(p.base_total ~ scavenger + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(bs1)
qqnorm(bs1)
xyplot(p.base_total ~ scavenger, data = dc.plot, type = c("p", "r"))
summary(bs1)
```



###p.bound v. fauna
```{r}
na1 <- lme(p.bound_total ~ abundance.x + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(na1)
qqnorm(na1)
summary(na1)
```
###p.bound v. herbivore
```{r}
nh1 <- lme(p.bound_total ~ herbivore + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(nh1)
qqnorm(nh1)
summary(nh1)
```

###p.bound v. predator
```{r}
np1 <- lme(p.bound_total ~ predator + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(np1)
qqnorm(np1)
summary(np1)
```

###p.bound v. scavenger
```{r}
ns1 <- lme(p.bound_total ~ scavenger + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(ns1)
qqnorm(ns1)
summary(ns1)
```

##p.total v. fauna
###p.total v. abundance
```{r}
ta1 <- lme(p.total ~ abundance.x + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(ta1)
xyplot(p.total~abundance, data = dc.plot)
qqnorm(ta1)
summary(ta1)
```
###p.total v. herbivore
```{r}
ha1 <- lme(p.total ~ herbivore + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(ha1)
xyplot(p.total ~ herbivore, data = dc.plot)
qqnorm(ha1)
summary(ha1)
```
##p.resin v. fauna
###p.resin v. abundance
```{r}
ap1 <- lme((log(p.resin)) ~ abundance + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.resin ~ abundance, data = dc.plot, group = field)
plot(ap1)
qqnorm(ap1)
summary(ap1)
```
###p.resin v. herbivore
```{r}
hr1 <- lme(log(p.resin) ~ herbivore + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.resin ~herbivore, data = dc.plot, group = field)
plot(hr1)
qqnorm(hr1)
summary(hr1)
```
###p.resin v. predator
```{r}
pr1 <- lme(log(p.resin) ~ predator + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.resin ~ predator, data = dc.plot, groups = field)
plot(pr1)
qqnorm(pr1)
summary(pr1)
```

###p.resin v. scavenger
```{r}
sr1 <- lme(log(p.resin) ~ scavenger + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.resin ~ scavenger, data = dc.plot)
plot(sr1)
qqnorm(sr1)
summary(sr1)
```

###p.total v. predator
```{r}
tp1 <- lme(p.total ~ predator + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(tp1)
xyplot(p.total ~ predator, data = dc.plot)
qqnorm(tp1)
summary(tp1)
```
###p.total v. scavenger
```{r}
ts1 <- lme(p.total ~ scavenger + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(ts1)
qqnorm(ts1)
xyplot(p.total ~scavenger, data = dc.plot)
summary(ts1)
```

#p.change v. micro
##p.h2o.change v. micro
###p.h2o.change v. respiration
```{r}
phr1 <- lme((p.h2o.change) ~ co2 + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.h2o.change ~ co2, data = dc.plot)
plot(phr1)
qqnorm(phr1)
summary(phr1)
```

###p.h2o.change v. biomass
```{r}
phc1 <- lme((p.h2o.change) ~ micro.c + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(phc1)
qqnorm(phc1)
summary(phc1)
```

###p.h2o.change v. phos
```{r}
php1 <- lme((p.h2o.change) ~ phos + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(php1)
xyplot(p.h2o.change ~ phos, data = dc.plot)
qqnorm(php1)
summary(php1)
```

##p.adsorb change v. micro
### p.adsorb change v. respiration
```{r}
arc1 <- lme(p.absorb.change ~ co2 + pH, random = ~1|field/block.x, data = subset(dc.plot, p.total > 875), na.action = na.omit)
summary(arc1)
plot(arc1)
qqnorm(arc1)
arc2 <- lm(p.absorb.change ~ co2 + pH + block, data = subset(dc.plot, p.total > 875))
summary(arc2)
plot(arc2)
```
###p.adsorb change v. biomass
```{r}
acc1 <- lme(p.absorb.change ~ micro.c + pH, random = ~1|field/block.x, data = subset(dc.plot, p.total > 875), na.action = na.omit)
summary(acc1)
plot(acc1)
qqnorm(acc1)
acc2 <- lm(p.absorb.change ~ micro.c + pH + block, data = subset(dc.plot, p.total > 875))
summary(acc2)
plot(acc2)
```
###p.absorb chagne v. phos
```{r}
acc1 <- lme(p.absorb.change ~phos + pH, random = ~1|field/block.x, data = subset(dc.plot, p.total > 875), na.action = na.omit)
summary(acc1)
plot(acc1)
qqnorm(acc1)
```


##p.bicarb.change v. micro
###p.bicarb.change v. co2
```{r}
occ1 <- lme((p.bicarb.change) ~ co2 + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
summary(occ1)
plot(occ1)
qqnorm(occ1)
```

###p.bicarb.chagne v. micro.c
```{r}
omc1 <- lme((p.bicarb.change) ~ micro.c + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
summary(omc1)
plot(omc1)
qqnorm(omc1)
```

###p.bicarb.change v. phos
```{r}
ocp1 <- lme((p.bicarb.change) ~ phos + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(ocp1)
qqnorm(ocp1)
summary(ocp1)
```

##p.base.change v. micro
###p.base chagne v. co2
```{r}
bcr1 <- lme((p.base.change) ~ co2 + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(bcr1)
qqnorm(bcr1)
xyplot(p.base.change ~ co2, data = dc.plot, group = field)
xyplot(p.base.change ~ co2 | field, data = dc.plot)
summary(bcr1)
```
###p.base change v. micro.c
```{r}
bcc1 <- lme((p.base.change) ~ micro.c + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(bcc1)
qqnorm(bcc1)
xyplot(p.base.change ~ micro.c, group = field, data = dc.plot)
summary(bcc1)
```

###p.base.change v. phos
```{r}
bcp1 <- lme((p.base.change) ~ phos + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
plot(bcp1)
qqnorm(bcp1)
xyplot(p.base.change ~ phos, group = field, data = dc.plot)
summary(bcp1)
```
##b.bound.change v. micro
###p.bound.change v. co2
```{r}
ucr1 <- lme((p.bound.change) ~ co2 + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.bound.change ~ co2, data = dc.plot, groups = field)
plot(ucr1)
qqnorm(ucr1)
summary(ucr1)
```

###p.base.change v. micro.c
```{r}
ucm1 <- lme((p.bound.change) ~ micro.c + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.bound.change ~ micro.c, groups = field, data = dc.plot)
plot(ucm1)
qqnorm(ucm1)
summary(ucm1)
```
###p.base.change v. phos
```{r}
ucp1 <- lme((p.bound.change) ~ phos + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.bound.change ~ phos, groups = field, data = dc.plot)
xyplot(p.bound.change ~ phos | field, data = dc.plot)
plot(ucp1)
qqnorm(ucp1)
summary(ucp1)
```



##p.total.change v. micro
###p.total change .v. respiration
```{r}
tcr1 <- lme((p.total.change) ~ co2 + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.total.change ~ co2, groups = field, data = dc.plot)
plot(tcr1)
qqnorm(tcr1)
summary(tcr1)
```

###p.total change v. micro.c
```{r}
tcm1 <- lme((p.total.change) ~ micro.c + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.total.change ~ micro.c, groups = field, data = dc.plot)
plot(tcm1)
qqnorm(tcm1)
summary(tcm1)
```


###p.total change v. phos
```{r}
tcp1 <- lme((p.total.change) ~ phos + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.total.change ~ phos, groups = field, data = dc.plot)
plot(tcp1)
qqnorm(tcp1)
summary(tcp1)
```



#p.change v. invert
##p.h2o.change v. invert
###delta.h2o v. total
```{r}
hca1 <- lme(p.h2o.change ~ abundance.x + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.h2o.change ~ abundance.x, group = field, data = dc.plot)
plot(hca1)
qqnorm(hca1)
summary(hca1)
```

###chang.h2o v. herb
```{r}
hch1 <- lme(p.h2o.change ~ herbivore + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.h2o.change ~ herbivore, group = field, data = dc.plot)
plot(hch1)
qqnorm(hch1)
summary(hch1)
```

###change.h2o v. pred

```{r}
hcp1 <- lme(p.h2o.change ~ predator + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.h2o.change ~ predator, group = field, data = dc.plot)
plot(hcp1)
qqnorm(hcp1)
summary(hcp1)
```

###h2o.change v. scavang
```{r}
hcs1 <- lme(p.h2o.change ~ scavenger + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.h2o.change ~ scavenger, group = field, data = dc.plot)
plot(hcs1)
qqnorm(hcs1)
summary(hcs1)
```

##p.absorb.change v. fauna
###p.absorb.change v. all
```{r}
aca1 <- lme(p.absorb.change ~ abundance.x + pH, random = ~1|field/block.x, data = subset(dc.plot, p.total > 875), na.action = na.omit)
xyplot(p.h2o.change ~ abundance.x, group = field, data = subset(dc.plot, p.total > 875))
plot(aca1)
qqnorm(aca1)
summary(aca1)
```
###p.absorb.change v. herbivore
```{r}
ach1 <- lme(p.absorb.change ~ herbivore + pH, random = ~1|field/block.x, data = subset(dc.plot, p.total > 875), na.action = na.omit)
xyplot(p.h2o.change ~ herbivore, group = field, data = subset(dc.plot, p.total > 875))
plot(ach1)
qqnorm(ach1)
summary(ach1)
```
###p.absorb chane v. predator
```{r}
acp1 <- lme(p.absorb.change ~ predator + pH, random = ~1|field/block.x, data = subset(dc.plot, p.total > 875), na.action = na.omit)

xyplot(p.h2o.change ~ herbivore, group = field, data = subset(dc.plot, p.total > 875))
plot(acp1)
qqnorm(acp1)
summary(acp1)
```
###p.absorb.change v. scavanger
```{r}
acp1 <- lme(p.absorb.change ~ scavenger + pH, random = ~1|field/block.x, data = subset(dc.plot, p.total > 875), na.action = na.omit)

xyplot(p.h2o.change ~ scavenger, group = field, data = subset(dc.plot, p.total > 875))
plot(acp1)
qqnorm(acp1)
summary(acp1)
```



##p.olsen.change v. fauna
###p.olsen.change v. all
```{r}
oca1 <- lme(p.bicarb.change ~ abundance.x + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.bicarb.change ~ abundance.x, group = field, data = dc.plot)
plot(oca1)
qqnorm(oca1)
summary(oca1)
```

###p.olsen.change v. herb
```{r}
och1 <- lme(p.bicarb.change ~ herbivore + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.bicarb.change ~ herbivore, group = field, data = dc.plot)
plot(och1)
qqnorm(och1)
summary(och1)
```

###p.olsen.change v. predator
```{r}
ocp1 <- lme(p.bicarb.change ~ predator + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.bicarb.change ~ predator, group = field, data = dc.plot)
plot(ocp1)
qqnorm(ocp1)
summary(ocp1)
```
###olsen.change v. scavenger
```{r}
ocs1 <- lme(p.bicarb.change ~ scavenger + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.bicarb.change ~ scavenger, group = field, data = dc.plot)
plot(ocs1)
qqnorm(ocs1)
summary(ocs1)
```

##base.change v fauna
###base.change v. all
```{r}
bca1 <- lme(p.base.change ~ abundance.x + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.base.change ~ abundance.x, group = field, data = dc.plot)
plot(bca1)
qqnorm(bca1)
summary(bca1)
```

###base change v. herb
```{r}
bch1 <- lme(p.base.change ~ herbivore + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.base.change ~ herbivore, group = field, data = dc.plot)
summary(bch1)
plot(bch1)
qqnorm(bch1)
```

###base change v. predator
```{r}
bcp1 <- lme(p.base.change ~ predator + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.base.change ~ predator, group = field, data = dc.plot)
plot(bcp1)
qqnorm(bcp1)
summary(bcp1)
```

###base change v. scavanger
```{r}
bcs1 <- lme(p.base.change ~ scavenger + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.base.change ~ scavenger, group = field, data = dc.plot)
qqnorm(bcs1)
plot(bcs1)
summary(bcs1)
```

##bound.change v. fauna
###bound chnage v. all
```{r}
uca1 <- lme(p.bound.change ~ abundance.x + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.bound.change ~ abundance.x, group = field, data = dc.plot)
plot(uca1)
qqnorm(uca1)
summary(uca1)
```

###bound change v. herb
```{r}
uch1 <- lme(p.bound.change ~ herbivore + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.bound.change ~ herbivore, group = field, data = dc.plot)
plot(uch1)
qqnorm(uch1)
summary(uch1)
```

###bound chagne v. pred
```{r}
ucp1 <- lme(p.bound.change ~ predator + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.bound.change ~ predator, group = field, data = dc.plot)
plot(ucp1)
qqnorm(ucp1)
summary(ucp1)
```

###p.bound.change v. scavenger
```{r}
ucs1 <- lme(p.bound.change ~ scavenger + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.bound.change ~ scavenger, group = field, data = dc.plot)
plot(ucs1)
qqnorm(ucs1)
summary(ucs1)
```

##p.total.change v. fauna
###p.total.change v. all
```{r}
tca1 <- lme(p.total.change ~ abundance.x + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.total.change ~ abundance.x, group = field, data = dc.plot)
plot(tca1)
qqnorm(tca1)
summary(tca1)
```

###p.total.change v. herb
```{r}
tch1 <- lme(p.total.change ~ herbivore + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.total.change ~ herbivore, group = field, data = dc.plot)
plot(tch1)
qqnorm(tch1)
summary(tch1)
```

###p.total chagne v. predator
```{r}
tcp1 <- lme(p.total.change ~ predator + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.total.change ~ predator, group = field, data = dc.plot)
plot(tcp1)
qqnorm(tcp1)
summary(tcp1)
```

###p.total change v. scavenger
```{r}
tcs1 <- lme(p.total.change ~ scavenger + pH, random = ~1|field/block.x, data = dc.plot, na.action = na.omit)
xyplot(p.total.change ~ scavenger, group = field, data = dc.plot)
plot(tcs1)
qqnorm(tcs1)
summary(tcs1)
```






#calculating which samples have statistically significant salt-adsorbed P pools
a statistically significant salt-absorbed P pool would be a sample where the pool is more than 2 standard deviations away from zero. 
```{r}
xyplot(p.k2so4 - p.h2o ~ p.total, data = dat)
t.test(dat$p.k2so4, dat$p.h2o, paired = TRUE, na.action = na.omit)
stdev <- sd(na.omit(dat$p.k2so4 - dat$p.h2o))
n <- length(na.omit(dat$p.k2so4 - dat$p.h2o))
se <- stdev/sqrt(n)
2*se
dat.sigab <- (subset(dat, p.absorb > stdev))
length(dat.sigab$p.k2so4)
m <- mean(na.omit(dat$p.k2so4 - dat$p.h2o))
xyplot(p.absorb ~ p.total, data = dat.sigab)
xyplot(p.k2so4 ~ p.h2o, data = dat)
max(dat$pH)
```


##soil microbes v. fauna
```{r}
xyplot(co2~abundance, data = dc.plot)
xyplot(co2~abundance | treat.stover.x, data = dc.plot, type = c("p", "r"))
xyplot(micro.c~abundance | treat.stover.x, data = dc.plot, type = c("p", "r"))
summary(lm(co2~abundance * treatment, data = dc.plot))
bwplot(toc.k2so4 ~ treatment|bout , data = dat)
bwplot(toc.h2o ~ treatment | bout, data = dat)
bwplot(c.percent ~ treatment | bout, data = dat)
bwplot(micro.c ~ treatment | bout + field, data = dat)
bwplot(p.h2o ~ factor(block) | bout, data = dat)
summary(lm(toc.k2so4 ~ treatment + bout, data = dat))
```

